03_DESeq_pit

### 2019-04-07 analysis/02_DESeq2_hyp.Rmd
now with 8000 limit

ggplot(dat, aes(V1, V2)) +
  geom_tile(aes(fill = V3)) +
  scale_fill_viridis(na.value="#FFFFFF00") + 
  xlab("Treatment") + ylab("Treatment") +
  labs(fill = "# of DEGs")
```

>>>>

ggplot(dat, aes(V1, V2)) +
  geom_tile(aes(fill = V3)) +
  scale_fill_viridis(na.value="#FFFFFF00", 
                     limits = c(0,8028)) + 
  xlab("Treatment") + ylab("Treatment") +
  labs(fill = "# of DEGs")
```

### 2019-04-07 analysis/03_DESeq2_pit.Rmd
now with 8000 limit

ggplot(dat, aes(V1, V2)) +
  geom_tile(aes(fill = V3)) +
  scale_fill_viridis(na.value="#FFFFFF00", 
                     limits = c(0,7914)) + 
  xlab("Timepoint") + ylab("Timepoint") +
  labs(fill = "# of DEGs")
```

>>>>

ggplot(dat, aes(V1, V2)) +
  geom_tile(aes(fill = V3)) +
  scale_fill_viridis(na.value="#FFFFFF00", 
                     limits = c(0,8028)) + 
  xlab("Timepoint") + ylab("Timepoint") +
  labs(fill = "# of DEGs")
```
